### 2022-05-18 chapters/execution_environement/execution_environement.tex
add : python
Revising Java

\chapter{Execution enviroment}
\label{chapter:enviroment}
After studying the impact of the programming languages choice on the energy consumption of softwares. we wanted to dig in more deeper. Therefore we have chosen two of the most popular programming lanaguages \textbf{Python} and \textbf{Java}
In this chapter we will reduce the energy consumption of those following lanaguages by doing some tuning
\import{chapters/execution_environement/java}{java}

>>>>

\chapter{Execution environment}
\label{chapter:enviroment}
After studying the impact of the programming languages choice on the energy consumption of software, we wanted to dig in more deeper.
Therefore, we have chosen two of the most popular programming languages \textbf{Python} and \textbf{Java}.
In this chapter, we explore the reduction of energy consumption of those languages by tuning their configuration.

\import{chapters/execution_environement/java}{java}
\import{chapters/execution_environement/python}{python}
